On optimisation in HDR brachytherapy

### 2015-03-05 Paper BMT/article-sample-proceedings.tex
LP start

\section{Genetic Algorithm}
The Genetic Algorithm as introduced in \citep{1} has a lot of paramters which are described in the following.

@@

\subsubsection{Scaling and Accuracy}
The dose distribution of a radioactive seed shows that the dose at a radius of 10 cm is negligible small. So any treatment range higher than 10 cm wouldn't lead to better results anyway. (TODO: which range is acceptable)
\begin{acknowledgement}
Please insert acknowledgments of the assistance of colleagues or similar notes of appreciation here.
\end{acknowledgement}

@@

>>>>

\section{Genetic Algorithm}
The Genetic Algorithm as introduced in \citep{1} has a lot of parameters which are described in the following.

@@

\subsubsection{Scaling and Accuracy}
The dose distribution of a radioactive seed shows that the dose at a radius of 10 cm is negligible small. So any treatment range higher than 10 cm wouldn't lead to better results anyway. (TODO: which range is acceptable)

\section{Linear Programming}
In Linear Programming a goal function and constraints are used to compute the optimal solution, as described in \citep{2}.

\subsection{Goal function and Constraints}
bla bla

\subsection{Results}
bla bla bla

\begin{acknowledgement}
Please insert acknowledgments of the assistance of colleagues or similar notes of appreciation here.
\end{acknowledgement}

@@

\bibitem{2}
Williams, H. Paul Model Building in Mathmetical Programming, 4th ed., 1999.
